Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2018-01-25 paper/aldebaran.tex
phrasing

Fortunately, this GP can be written as the solution of a class of stochastic
ordinary differential equations, the Continuous Auto-Regressive Moving Average
(CARMA) models, whose likelihoods can be evaluated in linear time. For problems
such as the damped driven harmonic oscillator, we therefore have access to these
powerful computational tools for inferring their power spectral densities.
\citet{Kelly2014} gives more details on CARMA processes in an astronomical
context, and shows how a state-space model of the solution $y(t)$ can be tracked
through a time-series of uncertain observations $y_k = y\left( t_k \right) +
\epsilon_k$, with Gaussian noise $\epsilon_k$ of zero mean and known
(heteroskedastic) variance, using a Kalman filter to produce a likelihood
function $p\left( y_k \mid \sigma, r_i, b_j \right)$ depending on the amplitude
of the stochastic forcing, $\sigma$, the (possibly complex) eigenfrequencies of
the ODE, $r_i$, and parameters describing the power spectrum of the stochastic
forcing, $b_j$ in $\mathcal{O}\left( n \right)$ computational time.
Additionally, \citet{Foreman-Mackey2017} show how a dimensional expansion can be
used to reduce the standard Gaussian Process covariance matrix for this same
process,  with autocorrelation given by Eq.\ \eqref{eq:CARMA-ACF} under
observations at times $t_k$, to a banded form that can then be
Cholesky-decomposed in the standard Gaussian Process likelihood function in
$\mathcal{O}\left( n \right)$ time.

>>>>

Fortunately, the damped and driven harmonic oscillator GP can be written as the solution of a class of stochastic ordinary differential equations, the Continuous Auto-Regressive Moving Average
(CARMA) models, whose likelihoods can be evaluated in linear time. For problems
such as this, we therefore have access to these
powerful computational tools for inferring their power spectral densities.
\citet{Kelly2014} gives more details on CARMA processes in an astronomical
context, and shows how a state-space model of the solution $y(t)$ can be tracked
through a time-series of uncertain observations $y_k = y\left( t_k \right) +
\epsilon_k$, with Gaussian noise $\epsilon_k$ of zero mean and known
(heteroskedastic) variance, using a Kalman filter to produce a likelihood
function $p\left( y_k \mid \sigma, r_i, b_j \right)$ depending on the amplitude
of the stochastic forcing, $\sigma$, the (possibly complex) eigenfrequencies of
the ODE, $r_i$, and parameters describing the power spectrum of the stochastic
forcing, $b_j$ in $\mathcal{O}\left( n \right)$ computational time.
Additionally, \citet{Foreman-Mackey2017} show how a dimensional expansion can be
used to reduce the standard Gaussian Process covariance matrix for this same
process,  with autocorrelation given by Eq.\ \eqref{eq:CARMA-ACF} under
observations at times $t_k$, to a banded form that can then be
Cholesky-decomposed in the standard Gaussian Process likelihood function in
$\mathcal{O}\left( n \right)$ time.
